% References
\renewcommand{\bibname}{مراجع}
\addcontentsline{toc}{chapter}{مراجع}

\begin{thebibliography}{99}

\begin{latin}

\baselineskip=.7cm

\bibitem{b7}
E. Baccour et al., "Pervasive AI for IoT Applications: A Survey on Resource-Efficient Distributed Artificial Intelligence," in \textit{IEEE Communications Surveys and Tutorials}, vol. 24, no. 4, pp. 2366-2418, Fourthquarter 2022, doi: 10.1109/COMST.2022.3200740.

\bibitem{b8}
A. A. Osuwa, E. B. Ekhoragbon and L. T. Fat, "Application of artificial intelligence in Internet of Things," in \textit{2017 9th International Conference on Computational Intelligence and Communication Networks (CICN)}, Girne, Northern Cyprus, 2017, pp. 169-173, doi: 10.1109/CICN.2017.8319379.

\bibitem{a10}
Dinh C. Nguyen, Ming Ding, Pubudu N. Pathirana, Aruna Seneviratne, “Federated Learning for Internet of Things:
A Comprehensive Survey”,\textit{arXiv:2104.07914v1}, 2021.

\bibitem{book_1}
Kairouz, P., McMahan, H.B., Avent, B., Bellet, A., Bennis, M., Bhagoji, A.N., Bonawitz,
K., Charles, Z., Cormode, G., and Cummings, R., “Advances and open problems in federated
learning”, \textit{Foundations and Trends® in Machine Learning}, vol. 14, no. 1–2, pp. 1-210, 2021.

\bibitem{b6}
\noindent H. Brendan McMahan, Eider Moore, Daniel Ramage, Seth Hampson, Blaise Aguera y Arcas, “Communication-Efficient Learning of Deep Networks from Decentralized Data” \textit{AISTATS}, Google, Inc., 2017.

\bibitem{b1}
Beutel, Daniel J and Topal, Taner and Mathur, Akhil and Qiu, Xinchi and Fernandez-Marques, Javier and Gao, Yan and Sani, Lorenzo and Kwing, Hei Li and Parcollet, Titouan and Gusmão, Pedro PB de and Lane, Nicholas D, “Flower: A Friendly Federated Learning Research Framework” \textit{arXiv preprint arXiv:2007.14390}
, 2020.

\bibitem{a1} 
Wang, Xingwei and Zhao, Hong and Zhu, Jiakeng, “GRPC: a communication cooperation mehanism in distributed systems”,  \textit{Association for Computing Machinery}, 1993.

\bibitem{b9} 
M. Galar, A. Fernández, E. Barrenechea, H. Bustince, F. Herrera, “An overview of ensemble methods for binary classifiers in multi-class problems: Experimental study on one-vs-one and one-vs-all schemes,” in \textit{Pattern Recognition}, vol. 44, no. 8, pp. 1761-1776, August 2011, Elsevier.

\bibitem{a11}
Liu, Yang and Fan, Tao and Chen, Tianjian and Xu, Qian and Yang, Qiang, “FATE: An Industrial Grade Platform for Collaborative Learning with Data Protection
”,\textit{JMLR.org}, 2021.

\bibitem{b12}
 J. Koetsier, “Smart Home: Apple Is The Fastest-Growing Connected Device Company,” Forbes, Aug 31, 2022

\bibitem{bookG} 
J. Brownlee, “Better Deep Learning: Train Faster, Reduce Overfitting, and Make Better Predictions,” Machine Learning Mastery, December 13, 2018.

\bibitem{a13} 
 Portnoy, A., Tirosh, Y., Hendler, D., “Towards Federated Learning With Byzantine-Robust Client Weighting”, \textit{arXiv:2004.04986v2}, 2021

\bibitem{SAFA}
Wentai Wu, Ligang He, Weiwei Lin, Rui Mao, Carsten Maple, Stephen Jarvis, “SAFA: a Semi-Asynchronous Protocol for Fast Federated Learning with Low Overhead”,
 \textit{arXiv:1910.01355v4}, v. 4, 2021.

\bibitem{n2} 
Geiping, J., Bauermeister, H., Dröge, H., Moeller, M., “Inverting Gradients – How easy is it to break privacy in federated learning?”, \textit{arXiv:2003.14053v2}, 2020

\bibitem{paper_4}
Mahmod, Ahmad and Caliciuri, Giuseppe and Pace, Pasquale and Iera, Antonio, ``Improving the Quality of Federated Learning Processes via Software Defined Networking", \textit{Association for Computing Machinery}, 2023.


\bibitem{edge1}
Abreha, Haftay Gebreslasie, Mohammad Hayajneh, and Mohamed Adel Serhani, "Federated Learning in Edge Computing: A Systematic Survey",\textit{Wireless Sensor Networks towards the Internet of Things}, Sensors 22, no. 2: 450 , 2022

\bibitem{edge2}
Dhurgham Hassan Mahlool, Mohammed Hamzah Abed, "A Comprehensive Survey on Federated Learning: Concept and Applications",\textit{Computer Vision and Pattern Recognition}, arXiv:2201.09384 , 2022

\bibitem{ref5} 
Tuo Zhang, Lei Gao, Chaoyang He, Mi Zhang, Bhaskar Krishnamachari, Salman Avestimehr, “Federated Learning for Internet of Things: Applications, Challenges, and Opportunities”, \textit{arXiv:2111.07494v4}, v. 4, 2022.

\bibitem{ref6}
 Zhi Zhou, Xu Chen, En Li, Liekang Zeng, Ke Luo, Junshan Zhang, “Edge Intelligence: Paving the Last Mile of Artificial Intelligence with Edge Computing”, \textit{arXiv:1905.10083v1}, v. 1, 2019.

\bibitem{ref7} 
 Andy Chen and Chaitanya Asawa, “Going beyond the bounding box with semantic segmentation”, \textit{The Gradient}, 2018.

\bibitem{ref8} 
Zewen Li, Wenjie Yang, Shouheng Peng, Fan Liu, “A Survey of Convolutional Neural Networks: Analysis, Applications, and Prospects”, \textit{arXiv:2004.02806v1}, v. 1, 2020.

\end{latin}



\bibitem{ref3}
طلائي مهتاب "	توسعه‌ي الگوريتم و بررسي عملكرد يادگيري پراكنده با حريم شخصي تفاضلي تطبيقي``، \textit{استقلال،} دانشگاه صنعتی اصفهان، شماره~۱۷۷۵۸، صص~27-34، ۱۴۰۱.

\bibitem{ref4} 
 بزرگ‌زاد علی, “بررسی روشهای حل مشکل ناهمگونی آماری در یادگیری فدرال”, \textit{سمینار کارشناسی ارشد هوش مصنوعی و رباتیکز}, دانشگاه صنعتی اصفهان, 1401. 

\end{thebibliography}

